Statistical Theory\\ Chess Dataset Analysis

### 2024-09-29 Article/Article.tex
updated article

\documentclass[conference]{IEEEtran}
\usepackage[table]{xcolor}
\usepackage{ifthen, xkeyval, tikz, calc}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
% \usepackage{svg}
\usepackage{subcaption}
\usepackage{float}
\usepackage{tikz}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\checkmark}%
\newcommand{\xmark}{\ding{55}}%

@@

% \let\marginpar\oldmarginpar
\setlength{\marginparwidth}{5cm}
% \newcommand{\Bnote}[1]{\textbf{[Boaz: #1]}}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage[colorinlistoftodos,prependcaption, textwidth=3cm]{todonotes}

@@

\section{Introduction}
Chess is one of humanity's oldest board games, played by two players on an $8\times8$ grid. Each player, controlling 16 pieces of their color, aims to checkmate the opponent's King, making it impossible for the King to escape capture. Unlike many games, chess does not involve luck or hidden information; the outcome is determined solely by the players' knowledge, strategy, and analytical skills.

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[table]{xcolor}

\usepackage{tikz, calc}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
% \usepackage{svg}
\usepackage{subcaption}
\usepackage{float}
\usepackage{booktabs}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\checkmark}%
\newcommand{\xmark}{\ding{55}}%

@@

% \let\marginpar\oldmarginpar
\setlength{\marginparwidth}{5cm}
% \newcommand{\Bnote}[1]{\textbf{[Boaz: #1]}}
\usepackage[colorinlistoftodos,prependcaption, textwidth=3cm]{todonotes}

@@

\section{Introduction}
Chess is one of humanity's oldest board games \cite{chesswiki}, played by two players on an $8\times8$ grid. Each player, controlling 16 pieces of their color, aims to checkmate the opponent's King, making it impossible for the King to escape capture. Unlike many games, chess does not involve luck or hidden information; the outcome is determined solely by the players' knowledge, strategy, and analytical skills.

@@

\section{Results}

\newpage
\bibliographystyle{IEEEtran}
\bibliography{references}
